Behavior Driven Development in Haskell

### 2012-05-22 paper.tex
adding terminology.

@@

Note: Kazu defines functions without signatures if they are simple enough.
And their signatures are automatically inserted by IDE (like ghc-mod) later.

>>>>

\section{Terminology}

\begin{description}
\item[unit test] TBD
\item[example] TBD
\item[property] TBD
\item[behavior] TBD
\item[documentation] Text written in Haskell comments and parsed by Haddock
\end{description}

@@

The authors are not fundamentalist.
If functions to be defined are simple enough,
we might implement them first withtout signatures.
And their signatures can be automatically
inserted by IDE (like ghc-mod) later
if Haskell compilers can infer correctly.
Also, we can cut and paste typical examples and their results
from Haskell interpreters to their document.
